---
title: Function Description and Installation of group.filterNA.summary
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# group.filterNA.summary

<!-- badges: start -->
<!-- badges: end -->

The goal of group.filterNA.summary is to take a column out of a data frame input and remove all NA values from that column. Next, it creates a summary table with the count of each value in the column.

## Installation

You can install the development version of group.filterNA.summary from [GitHub](https://github.com/) with:
```{r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-Marcella-Cross/group.filterNA.summary")
```
## Data
This is a snapshot of the data set. It is borrowed from the data teachr package - originally called vancouver_trees
```{r}
library(group.filterNA.summary)
head(treedata)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
group.filterNA.summary(treedata, "curb") #expect summary of curb yes vs. no

#more examples can be found in the function document called group.R
```
## Test Explanation
-The first test in the test-group.R document tests a number of numeric variables. The one called height_range_id is one that is considered continuous by r even though it only has values 1-10. 
-The second test has two intentional errors
-The third test has two categorical variables, one that includes NA values, and one that does not. 
