---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# assignment-b1-and-b2-Marcella-Cross

The goal of assignment-b1 is to create a useful function and create examples and tests for that function.

I chose to create a function called "group.filterNA.summary()" that will allow the user to group by a column in their dataset, filter out its NA values, and then create a summary table output of the counts of each value occurance. 

The input is in the form (data,"column"). This refers to the name of your data set followed by the name of the variable for which you need the summary table. The name of the column should be put into quotations.

This folder also includes the license information.


Assignment B2 creates a package called "group.filterNA.summary()" which takes a column and data frame input and removes all NA values from that column. Next, it creates a summary table with the count of each value in the column.

To Install this package: 
```{r}
library(group.filterNA.summary)
```

To run the tests and function you need the following libraries loaded:
```{r}
library(devtools)
library(datateachr)
library(dplyr)
library(tidyverse)
library(testthat)
library(digest)
library(magrittr)
```

